conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-24 paper/paper.Rmd
Updated intro and conclusion; improved wording

A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience.

@@

[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. at the sub-national level) in Australia.

@@

A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work.

@@

[ #TODO Change the following sentence, copied ad verbatim from JSS bizicount because I like it ] For now, however, we feel that our base `bizicount` package is sufficiently general to assist in estimating the models most often encountered by applied researchers.

>>>>

[ A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience. ]

@@

[ What else is covered in this paper? ] An example use-case for `conmat` is provided for a local government area (i.e. at the sub-national level) in Australia.
Also provided is an analysis pipeline to support conmat, [`syncomat`](https://github.com/idem-lab/syncomat), which generates synthetic contact matrices for 200 countries.

@@

[ A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work. ]

@@

[ #TODO Change concluding sentence. The following is copied ad verbatim from JSS bizicount because I like it ] For now, however, we feel that our base `bizicount` package is sufficiently general to assist in estimating the models most often encountered by applied researchers.
